Audio Transport

### 2017-05-18 paper/paper2.tex
Paper almost done

A video of my implimentation is available at.

@@

If one of the sources is time varying the source material quickly deteriorates.
Great for constant sounds.

>>>>

A video of my implimentation in action is available at.

@@

As seen in the implimentation video, the sound quality is good for many types of signals.

One of the most noticeable artifacts that still exists is the interference that results from a single pitch being mapped to many places.
As the note splits and moves to new locations it begins to interfere with itself.
This can cause a drop in volume at the very start or end of a transport.
This could be fixed by requiring that the mapping be fixed.

There are however sounds that the effect does not work for.
If we try to transport to audio which has rapid changes in pitch, the source material deteriorates quickly because the transport map is not consistent.
In certain settings however this can be used musically.
If for example the we are transporting between two sounds with relatively constant pitch.

But overall this the sound quality is good for many sounds.
It has the potential to be used by DJs looking for interesting ways to mix between songs, and musicians looking to create new sounds.
